A statistical analysis of a counterstrike game: Boston 2018

### 2021-01-27 inst/counterstrike.Rmd
cache this computationally expensive result
Zachary wants to be called zac not zach

```{r, zachslist}
zachslist <- list(
    round1 = c("Skadoodle","olofmeister","tarik","GuardiaN","RUSH",
         "rain", "Stewie2k","karrigan","autimatic","NiKo"),
    round2 = c("karrigan", "NiKo", "Stewie2K", "RUSH", "rain", "GuardiaN",
         "autimatic", "olofmeister"),
    round3 = c("rain","tarik","autimatic", "karrigan","RUSH","GuardiaN",
         "Stewie2K","NiKo","olofmeister"),
    round4 = c("rain","GuardiaN","karrigan", "NiKo","olofmeister"),
    round5 = c("olofmeister","rain","karrigan", "tarik","Stewie2K","autimatic"),
    round6 = c("GuardiaN","karrigan")
)
```

@@

```{r, useit}
H <- hyper2(pnames=c(team1,team2))
for(i in zachslist){
  H <- H + counterstrike_maker(team1,team2, deathorder=i)
}
```

@@

```{r, random2}

>>>>

```{r, zacslist}
zacslist <- list(
    round1 = c("Skadoodle","olofmeister","tarik","GuardiaN","RUSH",
         "rain", "Stewie2k","karrigan","autimatic","NiKo"),
    round2 = c("karrigan", "NiKo", "Stewie2K", "RUSH", "rain", "GuardiaN",
         "autimatic", "olofmeister"),
    round3 = c("rain","tarik","autimatic", "karrigan","RUSH","GuardiaN",
         "Stewie2K","NiKo","olofmeister"),
    round4 = c("rain","GuardiaN","karrigan", "NiKo","olofmeister"),
    round5 = c("olofmeister","rain","karrigan", "tarik","Stewie2K","autimatic"),
    round6 = c("GuardiaN","karrigan")
)
```

@@

```{r, useit}
H <- hyper2(pnames=c(team1,team2))
for(i in zacslist){
  H <- H + counterstrike_maker(team1,team2, deathorder=i)
}
```

@@

```{r, random2,cache=TRUE}
